\textbf{Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated}

### 2022-09-30 submission/manuscript.Rmd
update

<!-- Ambiguous stimuli and irrelevance of objective features -->
While not all simulations have achieved perfect realism [e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images, @mcdonnell2010face], it is fair to assume that these technical limitations will become negligible in the near future, in particular in the field of face generation and replacement [@nightingale2022; @tucciarelli2020; @moshel2022]. This fact, however, leads to a new issue: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgments regarding their nature?

@@

One hundred and three participants were recruited via *Prolific*, a crowd-sourcing platform recognized for providing high quality data [@peer2022]. The only inclusion criterion was a fluent proficiency in English to ensure that the experiment instructions would be well-understood. Participants were incentivised with a reward of about \textsterling 7.5 for completing the study, which took about 45 minutes to finish. Demographic variables (age, gender, sexual orientation, education and ethnicity) were self-reported on a voluntary basis.

We excluded 3 participants that failed 2 (>= 66\%) or more attention check questions. The final sample included 100 participants (Mean age = 27.9, SD = 8.5, range: [19, 66]; Sex: 48\% females, 52\% males).

@@

The analysis was carried out using *R 4.2* [@RCoreTeam2022], the *tidyverse* [@wickham2019], and the *easystats* collection of packages [@insightArticle; @bayestestRArticle; @performanceArticle; @parametersArticle; @correlationArticle]. As all the details, scripts and complimentary analyses are open-access, the manuscript will focus on significant results. In particular, given the statistical volatility of the findings, which itself could have been a testament to the shifting nature and inter-individuality of our sense of reality, the present study will concentrate on results that provide very strong evidence against the null hypothesis ($p <.01$).

@@

Only one image file yielded a strong simulation monitoring bias (> 85\%), being classified as fake in 87.4\% of trials. This image was removed from further analysis, leaving 108 trials per participant. On average, across participants, 44\% of images (95\% CI [0.12, 0.64]) were judged as fake and 56\% of images (95\% CI [0.36, 0.84]) as real. An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 9.0% for the participants and 9.6% for the stimuli.

While the delay of re-exposure of the stimulus did not have a significant effect on participants' beliefs of reality ($OR = 1.00$, $95\CI = [0.99, 1.00]$ ), judgement confidence was found to be negatively associated with re-exposure delay, but only when the faces were judged as real ($\beta = -0.006$, $95\% CI = [-0.1, 0.002]$, $p = .004$)

@@

Trustworthiness, adjusted for beauty and familiarity, had a predominantly significant positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the belief that a stimulus was real ($\beta_{poly1} = 6.44$, $95\% CI = [-0.11, 13.00]$, $z = 1.93$, $p = .0054$) for females only. No effect on confidence was found for males, whereas a quadratic relationship was found for females for both faces judged as real ($\beta_{poly2} = 6.14$, $95\% CI = [2.13, 10.14]$, $z = 3.00$, $p = .003$) as well as fake ($\beta_{poly2} =6.12$, $95\% CI = [1.49, 10.75]$, $z = 2.59$, $p = .001$), suggesting that non-trustworthy and highly trustworthy faces were rated with more confidence as real or fake than average faces.

We did not find any significant relationships for familiarity adjusted for beauty and trustworthiness ($R^2_{marginal}$ = 2.0%). However, a significant positive and linear relationship was found with the confidence in faces judged as real ($\beta_{poly1} = 9.98$, $95\% CI = [3.83, 16.13]$, $z = 3.18$, $p = .001$) and a negative linear relationship was found with those judged as fake ($\beta_{poly1} = -12.41$, $95\% CI = [-20.27, -4.54]$, $z = -3.09$, $p = .002$) for males only, suggesting that faces are judged as real with more confidence when they are familiar, and judged as fake with more confidence when they are unfamiliar.

@@

The models including the personality traits suggested that *Honesty-Humility* had a significant negative relationship with the confidence associated with real as well as fake judgements ($\beta_{real} = -1.62$, $95\% CI = [-2.55, -0.70]$, $z = -3.43$, $p < .001$; $\beta_{fake} = -1.16$, $95\% CI = [-2.09, -0.23]$, $z = -2.45$, $p = 0.014$). For trait narcissism, significant positive associations were found between the probability of judging faces as real and dimensions of narcissism such as *Acclaim Seeking* ($\beta = 2.24$, $95\% CI = [1.17, 4.27]$, $z = 2.44$, $p = .015$), and *Manipulativeness* ($\beta = 0.47$, $95\% CI = [0.25, 0.87]$, $z = -2.4$, $p = 0.017$). Confidence judgements also shared links with narcissism through various facets, such as a positive relationship between the confidence for both real and fake judgments with *Acclaim Seeking* ($\beta_{real} = 1.65$, $95\% CI = [0.59, 2.70]$, $z = 3.07$, $p =.002$; $\beta_{fake} = 1.62$, $95\% CI = [0.56, 2.68]$, $z = 3.00$, $p = .003$), and a negative relationship with *Authoritativeness* ($\beta_{real} = -1.57$, $95\% CI = [-2.58, -0.57]$, $z = -3.08$, $p = .002$; $\beta_{fake} = -1.49$, $95\% CI = [-2.50, -0.48]$, $z = -2.89$, $p = .004$).

Overall social anxiety levels (obtained from aggregating the 2 anxiety scales - *SIAS-6* and *SPS-6*), on the other hand, was significantly associated with the confidence in real judgements only ($\beta_{real} = -0.22$, $95\% CI = [-0.30, -0.14]$, $z = -5.29$, $p < .001$). Similarly, *Intolerance to Uncertainty* was also negatively associated with confidence judgements of faces being real ($\beta_{real} = -0.30$, $95\% CI = [-0.45, -0.15]$, $z = -3.88$, $p < .001$). In particular, confidence in real judgements was found to share predominantly significant positive links with the *Prospective Anxiety* dimension ($\beta_{real} = 1.43$, $95\% CI = [0.10, 2.76]$, $z = 2.10$, $p = .036$), although there was a negative association found with the *Inhibitory Anxiety* dimension ($\beta_{real} = -1.00$, $95\% CI = [-2.01, 0.02]$, $z = -1.93$, $p = 0.054$). There was also a largely significant positive relationship between the *Persecutory Ideation* dimension of *Paranoid Beliefs* with the probability of faces being judged as real ($\beta = 1.87$, $95\% CI = [0.99, 3.54]$, $z = 1.93$, $p = .054$). However, the negative relationship between confidence judgements and *Paranoid Beliefs* was only found for faces judged as real ($\beta_{real} = -0.21$, $95\% CI = [-0.29, -0.14]$, $z = -5.63$, $p < .001$).

@@

Questions pertaining to the attitude towards AI were reduced to 3 dimensions through factor analysis, labelled AI-Enthusiasm (loaded by items expressing interest and excitement in AI development and applications), AI-Realness (loaded by items expressing positive opinions on the ability of AI to create realistic material), and AI-Danger (loaded by items expressing concerns on the unethical misuse of AI technology). Whereas overall attitudes towards AI was found to be significantly and negatively associated with judgement confidence for real faces only ($\beta_{real} = -0.16$, $95\% CI = [-0.2, -0.13]$, $z = 8.90$, $p < .001$), suggesting that individuals with highly positive attitudes are less confident in rating faces as real, AI-Enthusiasm displayed a significant positive relationship with the confidence in both real and fake judgments ($\beta_{real} = 0.21$, $95\% CI = [0.02, 0.40]$, $z = 2.20$, $p = .028$; $\beta_{fake} = 0.31$, $95\% CI = [0.12, 0.50]$, $z = -8.90$, $p < 0.001$).

@@

<!-- Attractiveness: females -->
Although attractiveness did not seem to be the primary drive underlying simulation monitoring of face images, we do nonetheless report significant associations, with a different pattern observed depending on the participant's gender. The quadratic relationship found for female participants is aligned with our hypothesis that salient faces (i.e., rated as very attractive or very unattractive) are judged to be more real. The fact that this effect did not reach significance for beauty underlines that attractiveness judgment, and its role in simulation monitoring, is a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women [@buunk2002age; @qi2022gender]. This is further evidenced by the observation that female participants were more confident in their judgement of fake faces when they rated the given stimulus very high or low on beauty.

<!-- Attractiveness: males -->
Indeed, we found a significant positive linear relationship in male participants for both attractiveness and beauty on simulation monitoring, that we could interpret under an evolutionary lens. Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities [@qi2022gender; @fink2006facial; @buunk2002age]. However, while it is possible that the evolutionary weight associated with attractiveness skewed the perceived saliency towards attractive faces, rendering them significantly more salient than unattractive faces and in turn distorted the relationship with simulation monitoring, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging [@lou2015perceptual; @indovina2007dissociation] or physiological markers [in particular, heart rate deceleration, @skora2022functional].

@@

<!-- trustworthiness -->
Our results suggested that trustworthiness ratings linearly increased beliefs in realness for females only (for p-values around .05). Given the evidence positing that faces presented as real were rated as more trustworthy [@liefooghe2022faces; @hoogers2021effect; @balas2017], we expected such a link to be more strongly present for both genders. One of the underlying mechanisms that possibly contributed to this dimorphism could have been the increased risk-taking aversion reported in females [explained evolutionarily as a compromise to their reproductive potential, @van2020sex], to which perceived facial trustworthiness relates [@hou2019survival]. While this hypothesis seems justified, given that female participants' confidence judgements for both fake and real faces were highest when these faces were rated highly trustworthy and untrustworthy, for the hypothesis to hold true, faces judged as highly untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real. As such, further studies are needed to investigate the causes of the increased simulation monitoring sensitivity to trustworthiness in females.

<!-- familiarity -->
Contrary to our hypothesis, familiarity was not found to be significantly related to simulation monitoring decisions. Interestingly, however, there was a significant relationship between familiarity and confidence judegments only for males, who rated highly familiar faces as real and unfamiliar faces as fake with greater confidence. It is possible that the confidence judgements of females are less malleable, and thus less likely to be influenced by the variability in face familiarity. In fact, this observation is consistent with that of @kaplan2012effect, whose study showed female participants exhibited greater metacognitive awareness in a facial recall task. However, this has not been corroborated by recent research, which found gender differences in the opposite direction instead (males were significantly overconfident regardless of their performance accuracy and the experimental conditions) [@bailey2021gender; @herbst2020gender]. Furthermore, it is to be noted that the distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar. As such, future studies should clarify this point by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items before querying the simulation monitoring judgments.

@@

Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness was found to be associated with a higher probability of judging the face stimuli as real. Indeed, this finding is in line with recent research suggesting that narcissists are less likely to engage in cognitive strategies such as reflective thinking [@littrell2020overconfidently; @ahadzadeh2021social] and are more vigilant of their environment [@carolan2017searching; @grapsas2020and; @eddy2021self]. For instance, @de2019facial reports that participants with higher scores in narcissism were faster at accurately recognizing faces with neutral and low-intensity emotional expressions. This hence implies that individuals with greater narcissistic tendencies could have perceived the face images as more salient and engaged in less thoughtful information-processing, thereby leading to their increased perceptions of the displayed stimulus being real.

@@

<!-- AI attitudes -->
Despite the ubiquity of AI, the literature pertaining to the influence of people's AI attitudes on simulation monitoring is scarce. Contrary to our expectations, we did not find evidence for the role of participants' expectations regarding the capabilities of AI technology (in terms of the realism of its productions). Instead, we found that having a generally positive attitude towards AI was related to a decrease in confidence in real judgements. However, it should be noted that our data analyses found the attitudes towards AI scale was better explained as 3 latent dimensions rather than an aggregated score. Indeed, analysing the extracted factors separately revealed that only one's enthusiasm about AI technology was related to an increased confidence in simulation monitoring ratings. This could potentially be because participants with a highly positive attitude towards AI perceive themselves as having greater knowledge about AI and its capabilities [@said2022artificial], hence permitting themselves to be more confident in their simulation monitoring decisions. This result is in line with reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications [@@said2022artificial].

<!-- Social Anxiety, Paranoia and Uncertainty Intolerance -->
Unsurprisingly, individuals with more persecutory ideations (a form of paranoia where one believes they will be harmed by others, @buck2019capturing) were more likely to rate the faces presented as real relative to fake. Consistent with previous findings that persecutory delusions are predicted by a greater sense of presence in a VR environment [@freeman2005psychology], it is likely that people with higher levels of paranoia are more sensitive to social threat and thus perceive the face stimuli presented with greater salience and emotionality, hence increasing their beliefs of its realness [@fornells2015people; @freeman2003can]. However, higher levels of persecutory ideation, social anxiety and intolerance of uncertainty were related to lower confidence in real judgements. While this observation appears contradictory, it could be explained through the lens of fictional reappraisal, an emotion regulation strategy in which the belief that an emotional stimulus is not real is used as a mean to down-regulate the associated emotional reactions [@sperduti2017distinctive; @sperduti2016paradox; @singer2021cognitive]. Indeed, previous studies report that individuals with paranoia and anxiety engaged in more affective processing of external ambiguous stimuli [@fornells2015people]. This result is also in line with prior findings suggesting that the likelihood of reality beliefs decreased when pictures were emotional, as compared to when they were neutral [@makowski2016phenomenal]. As such, given the positive correlation between paranoia, social anxiety and uncertainty intolerance [@morrison2014moderating; @counsell2017intolerance; @barnby2020paranoia], it is possible that individuals high in such traits have greater interpersonal sensitivity and perceived the ambiguous face images with greater emotional reactivity, therefore having to engage in emotional regulation strategies that resulted in a lower confidence for real judgements.

>>>>

<!-- Ambiguous stimuli and irrelevance of objective features -->
While not all simulations have achieved perfect realism [e.g., Computer Generated Images - CGI in movies often lack certain key details that makes them visually distinct from real images, @mcdonnell2010face], it is fair to assume that these technical limitations will become negligible in the near future, particularly in the field of face generation and replacement [@nightingale2022; @tucciarelli2020; @moshel2022]. Such circumstance, however, leads to a new issue: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgments regarding their nature?

@@

One hundred and fifty participants were recruited via *Prolific*, a crowd-sourcing platform recognized for providing high quality data [@peer2022]. The only inclusion criterion was a fluent proficiency in English to ensure that the experiment instructions would be well-understood. Participants were incentivised with a reward of about \textsterling 7.5 for completing the study, which took about 45 minutes to finish. Demographic variables (age, gender, sexual orientation, education and ethnicity) were self-reported on a voluntary basis.

We excluded 5 participants that either failed 2 (>= 66\%) or more attention check questions, took an implausibly short time to finish the questionnaires or had incomplete responses. The final sample included 145 participants (Mean age = 28.3, SD = 9.0, range: [19, 66]; Sex: 48.3\% females, 51.0\% males, 0.7\% others).

@@

The analysis was carried out using *R 4.2* [@RCoreTeam2022], the *tidyverse* [@wickham2019], and the *easystats* collection of packages [@insightArticle; @bayestestRArticle; @performanceArticle; @parametersArticle; @correlationArticle]. As all the details, scripts and complimentary analyses are open-access, the manuscript will focus on significant results. In particular, given the statistical volatility of some of the findings, which itself could have been a testament to the shifting nature and inter-individuality of our sense of reality, the present study will concentrate on results that provide very strong evidence against the null hypothesis ($p <.01$).

@@

Only one image file yielded a strong simulation monitoring bias (> 85\%), being classified as fake in 88.7\% of trials. This image was removed from further analysis, leaving 108 trials per participant. On average, across participants, 44\% of images (95\% CI [0.12, 0.64]) were judged as fake and 56\% of images (95\% CI [0.36, 0.84]) as real. An intercept-only model with the participants and images as random factors showed that the Intraclass Correlation Coefficient (ICC), which can be interpreted as the proportion of variance explained by the random factors, was of 9.0% for the participants and 9.6% for the stimuli.

While the delay of stimulus re-exposure stimulus did not have a significant effect on participants' beliefs of reality ($OR = 1.00$, $95\CI = [0.99, 1.00]$ ), judgement confidence was found to be negatively associated with re-exposure delay when the faces were judged as real ($\beta = -0.006$, $95\% CI = [-0.1, 0.002]$, $p = .004$)

@@

Trustworthiness, adjusted for beauty and familiarity, had a predominantly positive and linear relationship ($R^2_{marginal}$ = 2.0%) with the belief that a stimulus was real ($\beta_{poly1} = 6.44$, $95\% CI = [-0.11, 13.00]$, $z = 1.93$, $p = .0054$) for females only. No effect on confidence was found for males, whereas a quadratic relationship was found for females for both faces judged as real ($\beta_{poly2} = 6.14$, $95\% CI = [2.13, 10.14]$, $z = 3.00$, $p = .003$) as well as fake ($\beta_{poly2} =6.12$, $95\% CI = [1.49, 10.75]$, $z = 2.59$, $p = .001$), suggesting that non-trustworthy and highly trustworthy faces were rated with more confidence than average faces.

We did not find any significant relationships for familiarity adjusted for beauty and trustworthiness ($R^2_{marginal}$ = 2.0%). However, a significant positive and linear relationship was found between familiarity and the confidence judgements of rating faces as real ($\beta_{poly1} = 9.98$, $95\% CI = [3.83, 16.13]$, $z = 3.18$, $p = .001$) whereas a negative linear relationship was found with those judged as fake ($\beta_{poly1} = -12.41$, $95\% CI = [-20.27, -4.54]$, $z = -3.09$, $p = .002$) for males only. This hence suggests that males more confidently judge faces as real with when they are familiar, and as fake when they are unfamiliar.

@@

The models including the personality traits suggested that *Honesty-Humility* had a significant negative relationship with the confidence associated with real as well as fake judgements ($\beta_{real} = -1.62$, $95\% CI = [-2.55, -0.70]$, $z = -3.43$, $p < .001$; $\beta_{fake} = -1.16$, $95\% CI = [-2.09, -0.23]$, $z = -2.45$, $p = 0.014$). For trait narcissism, significant positive associations were found between the probability of judging faces as real and dimensions of narcissism such as *Acclaim Seeking* ($\beta = 2.24$, $95\% CI = [1.17, 4.27]$, $z = 2.44$, $p = .015$), and *Manipulativeness* ($\beta = 0.47$, $95\% CI = [0.25, 0.87]$, $z = -2.4$, $p = 0.017$). Confidence judgements also shared significant links with narcissism through various facets, such as a positive relationship between the confidence for both real and fake judgments with *Acclaim Seeking* ($\beta_{real} = 1.65$, $95\% CI = [0.59, 2.70]$, $z = 3.07$, $p =.002$; $\beta_{fake} = 1.62$, $95\% CI = [0.56, 2.68]$, $z = 3.00$, $p = .003$), and a negative relationship with *Authoritativeness* ($\beta_{real} = -1.57$, $95\% CI = [-2.58, -0.57]$, $z = -3.08$, $p = .002$; $\beta_{fake} = -1.49$, $95\% CI = [-2.50, -0.48]$, $z = -2.89$, $p = .004$).

The *Paranoid Thinking* dimension of *Persecutory Ideation* was positively related to the probability of faces being judged as real ($\beta = 1.87$, $95\% CI = [0.99, 3.54]$, $z = 1.93$, $p = .054$). However, a negative relationship between confidence judgements and having paranoid beliefs was found for faces judged as real ($\beta_{real} = -0.21$, $95\% CI = [-0.29, -0.14]$, $z = -5.63$, $p < .001$). Social anxiety levels (obtained from aggregating the 2 social anxiety scales - *SIAS-6* and *SPS-6*), on the other hand, was significantly negatively related to confidence in real judgements only ($\beta_{real} = -0.22$, $95\% CI = [-0.30, -0.14]$, $z = -5.29$, $p < .001$). Similarly, *Intolerance to Uncertainty* was also negatively associated with confidence judgements of faces being real ($\beta_{real} = -0.30$, $95\% CI = [-0.45, -0.15]$, $z = -3.88$, $p < .001$). Specifically, although a negative association was observed between confidence in real judgements and the uncertainty intolerance dimension of *Inhibitory Anxiety* ($\beta_{real} = -1.00$, $95\% CI = [-2.01, 0.02]$, $z = -1.93$, $p = 0.054$), predominantly positive links were observed with its dimension of *Prospective Anxiety* ($\beta_{real} = 1.43$, $95\% CI = [0.10, 2.76]$, $z = 2.10$, $p = .036$).

@@

Questions pertaining to the attitude towards AI were reduced to 3 dimensions through factor analysis, labelled AI-Enthusiasm (loaded by items expressing interest and excitement in AI development and applications), AI-Realness (loaded by items expressing positive opinions on the ability of AI to create realistic material), and AI-Danger (loaded by items expressing concerns on the unethical misuse of AI technology). As such, although overall attitudes towards AI was found to be significantly and negatively associated with judgement confidence for real faces only ($\beta_{real} = -0.16$, $95\% CI = [-0.2, -0.13]$, $z = 8.90$, $p < .001$), suggesting that individuals with highly positive attitudes are less confident in rating faces as real, the extracted latent factor of AI-Enthusiasm instead displayed a significant positive relationship with the confidence in both real and fake judgments ($\beta_{real} = 0.21$, $95\% CI = [0.02, 0.40]$, $z = 2.20$, $p = .028$; $\beta_{fake} = 0.31$, $95\% CI = [0.12, 0.50]$, $z = -8.90$, $p < 0.001$).

@@

<!-- Attractiveness: females -->
Although attractiveness did not seem to be the primary drive underlying simulation monitoring of face images, we do nonetheless report significant associations, with a different pattern observed depending on the participant's gender. The quadratic relationship found for female participants is aligned with our hypothesis that salient faces (i.e., rated as very attractive or very unattractive) are judged to be more real. The fact that this effect did not reach significance for beauty underlines that attractiveness judgment, and its role in simulation monitoring, is a multidimensional construct that cannot be reduced to physical facial attractiveness, in particular for women [@buunk2002age; @qi2022gender]. In fact, when the given stimulus was rated very high or low on beauty, female participants were more confident in their judgement of fake faces only, suggesting that external beauty only partially explains the role attractiveness plays in simulation monitoring decisions.

<!-- Attractiveness: males -->
Alternatively, we found a significant positive linear relationship in male participants for both attractiveness and beauty on simulation monitoring, that we could interpret under an evolutionary lens. Specifically, males purportedly place more emphasis on facial attractiveness as a sign of reproductive potential, as compared with females, who tend to value characteristics signaling resource acquisition capabilities [@qi2022gender; @fink2006facial; @buunk2002age]. However, while it is possible that the evolutionary weight associated with attractiveness skewed the perceived saliency towards attractive faces, rendering them significantly more salient than unattractive faces and in turn distorted the relationship with simulation monitoring, future studies should test this saliency-based hypothesis by measuring constructs closer to salience and its effects, for instance using neuroimaging [@lou2015perceptual; @indovina2007dissociation] or physiological markers [in particular, heart rate deceleration, @skora2022functional].

@@

<!-- trustworthiness -->
Our results found a positive linear trend between trustworthiness and simulation monitoring for females only; suggesting trustworthiness ratings linearly increased their beliefs in realness. Given the evidence positing that faces presented as real were rated more trustworthy [@liefooghe2022faces; @hoogers2021effect; @balas2017], we expected such a link to be more clearly present for both genders. One of the underlying mechanisms that possibly contributed to this dimorphism could have been the increased risk-taking aversion reported in females [explained evolutionarily as a compromise to their reproductive potential, @van2020sex], to which perceived facial trustworthiness relates [@hou2019survival]. While this hypothesis justifies much of our findings, particularly considering female participants' confidence judgements for both fake and real faces were also highest when these faces were rated very trustworthy and untrustworthy, for the hypothesis to hold true, faces deemed untrustworthy should have appeared as even more salient (representing an evolutionary threat), and hence be judged as more real. As such, further studies are needed to investigate the causes of the increased simulation monitoring sensitivity to trustworthiness in females.

<!-- familiarity -->
Contrary to our hypothesis, familiarity was not found to be significantly related to simulation monitoring decisions. Interestingly, however, there was a significant relationship between familiarity and confidence judgements for males only, who rated highly familiar faces as real and unfamiliar faces as fake with greater confidence. Previous studies have typically shown females to be superior at face recognition [@mishra2019gender; @lewin2002sex], displaying higher levels of facial memory [@sommer2013sex] and exhibiting greater metacognitive awareness [@kaplan2012effect]. As such, it is possible that the confidence judgements of females are less malleable to variability in face familiarity. Indeed, metacognitive awareness has been associated with greater cognitive inflexibility [@mishra2019gender]. However, this has not been corroborated by recent research, which found gender differences in the opposite direction instead (males were significantly overconfident regardless of their performance accuracy and the experimental conditions) [@bailey2021gender; @herbst2020gender]. Furthermore, it is to be noted that the present study's distribution of familiarity ratings was strongly skewed, and only a low number of pictures was rated as highly familiar. As such, future studies should clarify this point by experimentally manipulating familiarity, for instance by modulating the amount of exposure to items before querying the simulation monitoring judgments.

@@

Notably, greater narcissistic tendencies in dimensions such as acclaim seeking and manipulativeness was found to be associated with a higher probability of judging the face stimuli as real. Indeed, this finding is in line with recent research suggesting that narcissists were more susceptible to fake news [@piksa2022cognitive; @sindermann2020short], possibly due to the fact that they were less likely to engage in cognitive strategies such as reflective thinking [@littrell2020overconfidently; @ahadzadeh2021social] and are more vigilant of their environment [@carolan2017searching; @grapsas2020and; @eddy2021self]. This hence implies that individuals with greater narcissistic tendencies could have perceived the face images as more salient and engaged in less thoughtful information-processing, leading to their increased perceptions of the displayed stimulus being real.

@@

<!-- AI attitudes -->
Despite the ubiquity of AI, the literature pertaining to the influence of people's AI attitudes on simulation monitoring is scarce. Contrary to our expectations, we did not find evidence for the role of participants' expectations regarding the capabilities of AI technology (in terms of the realism of its productions). Instead, we found that having a generally positive attitude towards AI was related to a decrease in confidence in real judgements. However, it should be noted that we found attitudes towards AI to be better understood via 3 latent dimensions rather than encompassed within an aggregated score. Indeed, examining the extracted factors separately revealed only one's enthusiasm about AI technology to be related to an increased confidence in simulation monitoring ratings. This could potentially be because participants with a highly positive attitude towards AI perceive themselves as having greater knowledge about AI and its capabilities [@said2022artificial], hence permitting themselves to be more confident in their simulation monitoring decisions. This result is in line with reports that AI attitudes interacts with people's perceived self-knowledge to influence their perception of the opportunities and risks accorded by AI applications [@@said2022artificial].

<!-- Social Anxiety, Paranoia and Uncertainty Intolerance -->
Unsurprisingly, individuals with more persecutory ideations (a form of paranoia where one believes others intend to cause them harm, @buck2019capturing) were more likely to rate the faces presented as real relative to fake. Consistent with previous findings that persecutory delusions are predicted by a greater sense of presence in a VR environment [@freeman2005psychology], it is likely that people with higher levels of paranoia are more sensitive to social threat and thus perceive the face stimuli presented with greater salience and emotionality, hence increasing their beliefs of its realness [@fornells2015people; @freeman2003can]. However, higher levels of persecutory ideation, social anxiety and intolerance of uncertainty were related to lower confidence in real judgements. While such results appear contradictory, it could be explained through the lens of fictional reappraisal, an emotion regulation strategy in which the belief that an emotional stimulus is not real is used as a mean to down-regulate the associated emotional reactions [@sperduti2017distinctive; @sperduti2016paradox; @singer2021cognitive]. Indeed, previous studies report that individuals with paranoia and anxiety engaged in more affective processing of external ambiguous stimuli [@fornells2015people]. This result is also in line with prior findings suggesting that the likelihood of reality beliefs decreased when pictures were emotional, as compared to when they were neutral [@makowski2016phenomenal]. As such, given the positive correlation between paranoia, social anxiety and uncertainty intolerance [@morrison2014moderating; @counsell2017intolerance; @barnby2020paranoia], it is possible that individuals high in such traits have greater interpersonal sensitivity and perceived the ambiguous face images with greater emotionality, therefore having to engage in emotional regulation strategies that resulted in a lower confidence for real judgements.
